% UC Bio-bib Proceedings Table
% Created on 2022-12-23 10:09

\begin{longtable}{lp{9.0cm}p{4.5cm}}
Month/Year & Title & Meeting/Venue (Place)\\
\hline 
\endfirsthead


\multicolumn{3}{c}%
{{Conference Posters and Presentations - continued from previous page }} \\ \\
Month/Year & Title & Meeting/Venue (Place)\\
\hline 
\endhead

\\
\multicolumn{3}{c}%
{{ Conference Posters and Presentations continued on next page }} \\
\endfoot

\hline \hline
\endlastfoot

 
12/2021 & {\bf oupled Vegetation-Hydroclimatic Dynamics Across East Africa, Drivers of Prediction Skill in Cropland Regions, and Implications for Drought Early Warning}.   (Invited)  & American Geophysical Union Fall Meeting. (Virtual) \\
  
12/2021 & {\bf Flow Permanence Along Ephemeral Streams in the Huachuca Sky Island, Arizona and its Consequences for Vegetation Distribution}.   (Invited)  & American Geophysical Union Fall Meeting. (Virtual) \\
  
12/2021 & {\bf Water Stress in Riparian Woodlands from Groundwater Decline and Climate Change Ecosystem Indicators at Multiple Scales}.   (Invited)  & American Geophysical Union Fall Meeting. (Virtual) \\
  
12/2021 & {\bf Leveraging High-resolution Gridded Datasets and AquaCrop to Improve Remote Sensing-based Estimates of Smallholder Maize Yields}.   (Invited)  & American Geophysical Union Fall Meeting. (Virtual) \\
  
12/2021 & {\bf Hydroclimatic Controls on Phenology for Functional Plant Types in Drylands of the Southwest USA}.   (Invited)  & American Geophysical Union Fall Meeting. (Virtual) \\
  
12/2021 & {\bf Monitoring Water Stress of Southern California Plant Species During the 2013 2015 Drought Using Hyperspectral and Thermal Airborne Imagery}.   (Invited)  & American Geophysical Union Fall Meeting. (Virtual) \\
  
12/2021 & {\bf Drought Responsiveness of Evapotranspiration in Dryland Riparian Vegetation}.   (Invited)  & American Geophysical Union Fall Meeting. (Virtual) \\
  
12/2021 & {\bf Phenological Classification and Atmospheric Drought Response of Riparian Vegetation in Drylands of the Southwestern United States}.   (Invited)  & American Geophysical Union Fall Meeting. (Virtual) \\
  
12/2021 & {\bf Experimental and Numerical Investigation of Flux Partitioning methods for water vapor and carbon dioxide}.   (Invited)  & American Geophysical Union Fall Meeting. (Virtual) \\
  
12/2021 & {\bf A novel UAV-based approach for estimating evapotranspiration from thermal imagery at multiple scales}.   (Invited)  & American Geophysical Union Fall Meeting. (Virtual) \\
  
9/2021 & {\bf RF Backscatter-Based Sensors for Structural Health Monitoring}.   (Invited)  & International Balkan Conference on Communications and Networking (BalkanCom). () \\
  
3/2022 & {\bf Diurnal and seasonal variation in ET at canopy scales using a novel UAV-based approach}.   (Invited)  & European Geophysical Union General Assembly Conference. (Vienna) \\
  
3/2022 & {\bf Extreme heat impacts on food security in Africa}.   (Invited)  & European Geophysical Union General Assembly Conference. (Vienna) \\
 \end{longtable}

